Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Fixing up some citations.

It is important to recognize from this definition that \emph{any}
allocation strategy is an abstract
interpretation~\cite{MIGHTANDMANOLIOS}.  In particular, concrete
interpretation is a kind of abstract interpretation.  So is an
interpretation that allocates a single cell into which all bindings
and continuations are stored.  On the one hand is an abstract
interpretation that is non-computable and gives only the ground truth
of a programs behavior; on the other is an abstract interpretation
that is easy to compute but gives little information.  Useful program
analyses lay somewhere in between and can be characterized by their
choice of address representation and allocation strategy.

@@

Vardoulakis and Shivers evaluate their CFA2
analyzer~\cite{dvanhorn:Vardoulakis2011CFA2} against a variant of 0-CFA
defined in their framework.  [NEED TIMING FOR 0-CFA ON CHURCH.]  The
Church example is the largest benchmark Vardoulakis and Shivers
consider.  More work would be required to scale the analyzer to the
set of features required by our benchmarks.

@@

The only analyzers we were able to find that proved capable of
analyzing the full suite of benchmarks considered here were the Soft
Typing system of Wright [CITE] and, in many ways its successor, the
Polymorphic splitting system of Wright and
Jagannathan~\cite{dvanhorn:wright-jagannathan-toplas98}.\footnote{This
  is not a coincidence; these papers set a high standard for
  evaluation, which we consciously aimed to approach.  Many of our
  benchmarks are drawn from these papers.}  Unfortunately, these
analyses compute an inherently different and uncomparable form of
analysis.  Consequently, we have omitted a complete comparison with
these implementations,.  The AAM approach provides more precision in
terms of temporal-ordering of program states, which comes at a cost
that can be avoided in constraint-based approaches.  Consequently
implementation techniques cannot be ``ported'' between these two
approaches.  However, our optimized implementation is within an order
of magnitude of the performance of Wright and Jaganathan's analyzer.
Although we would like to improve this to be more competitive, the
optimized AAM approach still has many strengths to recommend it in
terms of precision, ease of implementation and verification, and rapid
design.

>>>>

It is important to recognize from this definition that \emph{any}
allocation strategy is an abstract
interpretation~\cite{dvanhorn:Might2009Posteriori}.  In particular,
concrete interpretation is a kind of abstract interpretation.  So is
an interpretation that allocates a single cell into which all bindings
and continuations are stored.  On the one hand is an abstract
interpretation that is non-computable and gives only the ground truth
of a programs behavior; on the other is an abstract interpretation
that is easy to compute but gives little information.  Useful program
analyses lay somewhere in between and can be characterized by their
choice of address representation and allocation strategy.

@@

Vardoulakis and Shivers evaluate their CFA2
analyzer~\cite{dvanhorn:Vardoulakis2011CFA2} against a variant of
0-CFA defined in their framework and the example we draw on is the
largest benchmark Vardoulakis and Shivers consider.  More work would
be required to scale the analyzer to the set of features required by
our benchmarks.

@@

The only analyzers we were able to find that proved capable of
analyzing the full suite of benchmarks considered here were the Soft
Typing system of Wright and
Cartwright~\cite{dvanhorn:Wright1997Practical} and, in many ways its
successor, the Polymorphic splitting system of Wright and
Jagannathan~\cite{dvanhorn:wright-jagannathan-toplas98}.\footnote{This
  is not a coincidence; these papers set a high standard for
  evaluation, which we consciously aimed to approach.  Many of our
  benchmarks are drawn from these papers.}  Unfortunately, these
analyses compute an inherently different and uncomparable form of
analysis.  Consequently, we have omitted a complete comparison with
these implementations,.  The AAM approach provides more precision in
terms of temporal-ordering of program states, which comes at a cost
that can be avoided in constraint-based approaches.  Consequently
implementation techniques cannot be ``ported'' between these two
approaches.  However, our optimized implementation is within an order
of magnitude of the performance of Wright and Jaganathan's analyzer.
Although we would like to improve this to be more competitive, the
optimized AAM approach still has many strengths to recommend it in
terms of precision, ease of implementation and verification, and rapid
design.
